Results

### 2018-03-17 02_analysis.Rmd
Add analysis of donation likelihood

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

# m_propensity_small <- stan_glm(donate_likely_bin ~ crackdown + issue + funding + 
#                                  crackdown * issue + crackdown * funding + issue * funding +
#                                  crackdown * issue * funding,
#                                data = results, family = binomial(link = "logit"),
#                                prior = student_t(df = 1, location = 0),
#                                prior_intercept = student_t(df = 1, location = 0),
#                                chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
```

```{r models-table, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

@@

@@

>>>>

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
```

```{r tbl-models-amount, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r build-models-likely, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
# Weakly informative normal priors, since these coefficients are log-odds
m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                       data = results, family = binomial(link = "logit"),
                       prior = normal(-1, 1),
                       prior_intercept = normal(-1, 1),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)

m_likely_cif <- update(m_likely_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_likely_c_full <- update(m_likely_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_likely_ci_full <- update(m_likely_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_likely_cif_full <-update(m_likely_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
```

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r likely-median-c}
newdata_conditions_c <- results %>% expand(nesting(crackdown))

# transform = TRUE does the same thing as plogis(as.matrix(m_likely_c))
chains_fitted_likely_c <- posterior_linpred(m_likely_c, 
                                            newdata = newdata_conditions_c, 
                                            transform = TRUE)

coef_summary_likely_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_c), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_likely_c <- ggplot(coef_summary_likely_c, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

```{r likely-median-ci}
newdata_conditions_ci <- results %>% expand(nesting(crackdown, issue))

chains_fitted_likely_ci <- posterior_linpred(m_likely_ci, 
                                             newdata = newdata_conditions_ci,
                                             transform = TRUE)

coef_summary_likely_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_ci), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_likely_ci <- ggplot(coef_summary_likely_ci, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_blue) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  # coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue)
```

```{r likely-median-cif}
newdata_conditions_cif <- results %>% expand(nesting(crackdown, issue, funding))

chains_fitted_likely_cif <- posterior_linpred(m_likely_cif, 
                                              newdata = newdata_conditions_cif,
                                              transform = TRUE)

coef_summary_likely_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_cif), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_likely_cif <- ggplot(coef_summary_likely_cif, aes(y = estimate, x = crackdown)) + 
  # geom_point(data = results, aes(y = amount_donate, x = crackdown),
  #            color = "grey50", size = 0.5, alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_red) +
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ issue + funding)
```

```{r plot-all-likely-medians, fig.width=8, fig.height=6}
((plot_likely_c + 
   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_likely_ci) | plot_likely_cif
```

@@

```{r likely-diffs-c}
diffs_coef_likely_pairs_c <- chains_fitted_likely_c %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_c$crackdown)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_likely_pairs_detail_c <- tidy_diffs(diffs_coef_likely_pairs_c)

pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_likely_c <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_c, aes(x = value),
               fill = ngo_green, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_c, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_c, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)
```

```{r likely-diffs-ci}
# Nest each fitted chain into a single row that corresponds to each newdata_condition
chains_nested_likely_ci <- chains_fitted_likely_ci %>% 
  as_data_frame() %>% 
  mutate(id = 1:n()) %>% 
  gather(condition, value, -id) %>% 
  group_by(condition) %>% 
  nest()

# Add the fitted chains to the conditions, spread the main crackdown condition
# into two columns, then nest everything by issue
all_chains_likely_ci <- bind_cols(newdata_conditions_ci, 
                                  chains_nested_likely_ci) %>% 
  unnest(data) %>% 
  select(-condition) %>% 
  group_by(issue) %>% 
  spread(crackdown, value) %>% 
  select(-id) %>% 
  nest()

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_ci <- all_chains_likely_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_likely_pairs_detail_ci <- pairs_likely_conditions_ci %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
  select(issue, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_likely_ci <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_ci, aes(x = value),
               fill = ngo_blue, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_ci, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_ci, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + pair)
```

```{r likely-diffs-cif}
# Nest each fitted chain into a single row that corresponds to each newdata_condition
chains_nested_likely_cif <- chains_fitted_likely_cif %>% 
  as_data_frame() %>% 
  mutate(id = 1:n()) %>% 
  gather(condition, value, -id) %>% 
  group_by(condition) %>% 
  nest()

# Add the fitted chains to the conditions, spread the main crackdown condition
# into two columns, then nest everything by issue
all_chains_likely_cif <- bind_cols(newdata_conditions_cif, 
                                   chains_nested_likely_cif) %>% 
  unnest(data) %>% 
  select(-condition) %>% 
  group_by(issue, funding) %>% 
  spread(crackdown, value) %>% 
  select(-id) %>% 
  nest()

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_cif <- all_chains_likely_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_likely_pairs_detail_cif <- pairs_likely_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
  select(issue, funding, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_likely_cif <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
               fill = ngo_red, colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_cif, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
((plot_diffs_likely_c + 
   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_likely_ci) | plot_diffs_likely_cif
```

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
  pandoc.table(missing = "—", 
               caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions')
```
